### 2019-04-21 sections/introconclude/intro.tex
bib test sync zotero overleaf

\newcommand{\introfootone}{For example, \textcite{gine_access_2011, KARAIVANOV2018100} use the initial waves of the Townsend Thai village survey to study how household firms choose between formal and informal borrowing in two-period models. \textcite{gine_access_2011} distinguishes formal and informal borrowing by interest rates, fixed costs, and collateral constraints.}

It is well known that in village economies, local informal financial arrangements exist in the absence of external formal credit market options \autocite{udry_risk_1994, townsend_risk_1994}. As formal borrowing and savings opportunities have expanded, informal credit markets have persisted. But dynamic models that study the effects of financial deepening on development do not explicitly consider informal financial options, and studies that test the fit of informal risk-sharing models to data generally do not consider formal options explicitly.\footnote{See \textcite{townsend_financial_2010, BKSannualReview} for reviews.} On the other hand, studies which explicitly analyze the interaction of formal and informal credit markets generally do so in non-dynamic settings.\footnote{\introfootone} It is difficult to fully analyze the effects of financial deepening which determines asset distributions, however, when these distributions are fixed. In this paper, I develop and estimate a dynamic equilibrium risky entrepreneur model that incorporates formal as well as informal borrowing and savings choices. In this model, households are infinitely-lived, risk-averse, and have varying productivity and \CZH.

>>>>

\newcommand{\introfootone}{For example, \textcite{gine_access_2011, karaivanov_disadvantages_2018} use the initial waves of the Townsend Thai village survey to study how household firms choose between formal and informal borrowing in two-period models. \textcite{gine_access_2011} distinguishes formal and informal borrowing by interest rates, fixed costs, and collateral constraints.}

It is well known that in village economies, local informal financial arrangements exist in the absence of external formal credit market options \autocite{udry_risk_1994, townsend_risk_1994}. As formal borrowing and savings opportunities have expanded, informal credit markets have persisted. But dynamic models that study the effects of financial deepening on development do not explicitly consider informal financial options, and studies that test the fit of informal risk-sharing models to data generally do not consider formal options explicitly.\footnote{See \textcite{townsend_financial_2010, buera_entrepreneurship_2015} for reviews.} On the other hand, studies which explicitly analyze the interaction of formal and informal credit markets generally do so in non-dynamic settings.\footnote{\introfootone} It is difficult to fully analyze the effects of financial deepening which determines asset distributions, however, when these distributions are fixed. In this paper, I develop and estimate a dynamic equilibrium risky entrepreneur model that incorporates formal as well as informal borrowing and savings choices. In this model, households are infinitely-lived, risk-averse, and have varying productivity and \CZH.

### 2019-04-21 sections/introconclude/literature.tex
bib test sync zotero overleaf

The analysis in this paper contributes to several strands of the literature. First, there has been substantial research on the impacts of greater financial access on developing economies \autocite{greenwood_financial_1990, banerjee_occupational_1993, lloyd-ellis_enterprise_2000, gine_evaluation_2004, greenwood_financing_2010, kaboski_structural_2011, moll_productivity_2014, buera_macroeconomics_2012, NBERw20821}. Despite the importance of informal financial arrangements \autocite{udry_risk_1994, townsend_risk_1994}, these dynamic models of financial deepening--formal credit market expansion--generally do not explicitly consider informal financial options.\footnote{\textcite{banerjee_credit_2017} allow households to borrow from formal and informal sectors at exogenous rates to finance within period capital investments, and households can save across periods at an exogenous negative savings rate.} Additionally, studies that test the fit of informal risk-sharing models to data do not model formal options explicitly \autocite{alem_evaluation_2014, karaivanov_dynamic_2014, KinnanThai}. In this paper, I model risky entrepreneurs' choices over formal and informal credit market options in an exogenous incomplete markets setting.\footnote{While there are different ways for rural households to transfer financial resources, \textcite{karaivanov_dynamic_2014} find that a model with exogenously incomplete borrowing and savings options fit consumption and investment data in rural Thai villages better than constrained efficient credit/insurance models. The model in effect augments equilibrium models of risky entrepreneurs (see review: \textcite{quadrini_entrepreneurship_2009}) with additional exogenous borrowing and savings options.} Similar to \textcite{kaboski_structural_2011}, I treat villages as small open economies where formal prices are exogenously determined, but I extend the framework to explicitly consider informal choices and equilibrium interest rates determined within each local informal credit market. My approach here focuses on the \textit{micro-equilibrium} effects of formal credit market expansion on village credit markets. This is different from \textcite{buera_macroeconomics_2012, BrezaKinnanNBERw24329}, which study the macro equilibrium effects of large microfinance roll-outs on prices, including interest rates and wages, in the aggregate economy.

Second, this paper contributes to works that study the interaction between formal and informal credit markets. Third, there is a significant and growing empirical literature that analyzes separate dimensions of credit market policies. Fourth, there is a literature that studies how the provision of formal insurance could crowd-out informal insurance \autocite{attanasio_consumption_2000,krueger_public_2011,ChandrasekharKinnanLarreguy}.

>>>>

The analysis in this paper contributes to several strands of the literature. First, there has been substantial research on the impacts of greater financial access on developing economies \autocite{greenwood_financial_1990, banerjee_occupational_1993, lloyd-ellis_enterprise_2000, gine_evaluation_2004, greenwood_financing_2010, kaboski_structural_2011, moll_productivity_2014, buera_macroeconomics_2012, dabla-norris_distinguishing_2018}. Despite the importance of informal financial arrangements \autocite{udry_risk_1994, townsend_risk_1994}, these dynamic models of financial deepening--formal credit market expansion--generally do not explicitly consider informal financial options.\footnote{\textcite{banerjee_credit_2017} allow households to borrow from formal and informal sectors at exogenous rates to finance within period capital investments, and households can save across periods at an exogenous negative savings rate.} Additionally, studies that test the fit of informal risk-sharing models to data do not model formal options explicitly \autocite{alem_evaluation_2014, karaivanov_dynamic_2014, kinnan_distinguishing_2017}. In this paper, I model risky entrepreneurs' choices over formal and informal credit market options in an exogenous incomplete markets setting.\footnote{While there are different ways for rural households to transfer financial resources, \textcite{karaivanov_dynamic_2014} find that a model with exogenously incomplete borrowing and savings options fit consumption and investment data in rural Thai villages better than constrained efficient credit/insurance models. The model in effect augments equilibrium models of risky entrepreneurs (see review: \textcite{quadrini_entrepreneurship_2009}) with additional exogenous borrowing and savings options.} Similar to \textcite{kaboski_structural_2011}, I treat villages as small open economies where formal prices are exogenously determined, but I extend the framework to explicitly consider informal choices and equilibrium interest rates determined within each local informal credit market. My approach here focuses on the \textit{micro-equilibrium} effects of formal credit market expansion on village credit markets. This is different from \textcite{buera_macroeconomics_2012, breza_measuring_2018}, which study the macro equilibrium effects of large microfinance roll-outs on prices, including interest rates and wages, in the aggregate economy.

Second, this paper contributes to works that study the interaction between formal and informal credit markets. Third, there is a significant and growing empirical literature that analyzes separate dimensions of credit market policies. Fourth, there is a literature that studies how the provision of formal insurance could crowd-out informal insurance \autocite{attanasio_consumption_2000,krueger_public_2011,chandrasekhar_information_2011}.
